Visual Interrogation of Attention-Based Models: \\ Applications in Language Inference and Machine Comprehension

### 2018-05-27 EMNLP-demo-paper/intro.tex
cleanup paper layout
updates in intro

Neural networks have been successful in various natural language processing tasks,
where end-to-end training become a primary option (cite).
As the design of neural networks evolve, there is a clear trend that more and more
parameters participate in training and prediction. While the strong expressivity
enhance model performance, the lack of interpretability presents challenging for analysis.
Without understanding the background meaning that features carry, visualization relies
on proper quantification analysis (cite). Such analysis is not easy to come up with,
and is tied to specific task (cite).

@@

To facilitate exploration in attention models, we introduce an interactive visualization toolset.

>>>>

Neural networks have been successful in various natural language processing tasks,
where end-to-end training become a primary option (\cite{}).
As the design of neural networks evolve, there is a clear trend that more and more
parameters participate in training and prediction. While the strong expressivity
enhance model performance, the lack of interpretability presents challenge for analysis.
Without understanding the background meaning that features carry, visualization relies
on proper quantification analysis (cite). Such analysis is not easy to come up with,
and is tied to specific task (cite).

@@

To facilitate exploration in attention models, we introduce an interactive visualization toolset
for word-attention models. We demonstrate our system on two primary NLP tasks: natural language
inference (NLI) and machine comprehension (MC). For the NLI task, we visualize
decomposable attention networks which represents a series of strongly performing models \cite{}.
For the MC task, we present your visualization methods on bidirectional attention flow model,
which also represents a line of strong models \cite{}.

In summary, our contribution in this papers are:
\begin{itemize}
	\item 1. We present an interactive visualization system for word-attention neural
	networks in NLP. Our system allows to...
	\item 2. We demonstrate our system on two major NLP tasks with strong-performing
	models. We observe functional limitations of these models which can be helpful
	for future improvement on modeling.
\end{itemize}
